\makeDedication{Dedicated to \textbf{Dr. Marion Edward Wilson} for giving me sight.}

\vspace{0.35cm}

\noindent This thesis summarizes the final year of my three years of undergraduate research.
As my journey comes to an end, the heart full of gratitude, I remember the people who made
it all possible.

My friends never left my side, no matter the distance. Antoine, while I was blind
and locked down at dusk, researched fish excavation, as kernel-level move semantics
ushered to us cryptic, yet ominous, blue-tinted words.
%
Raphaël grounded me in the present moment and never ceased to cultivate me.
%
McKay and Lily, serving courtside, gave me force over time, finding our
lives forever changed after dispassionately standing in line, stumbling upon an empty
parking lot.
%
Emiliano, an acquaintance of mine, ought to be thanked for his music, and for
volunteering to drive, only that one time, when it was only somewhat late,
dark, foggy, and raining outside. Though there may be competition from other
places, there is nobody I would rather be lost in space with, near a national park,
rocket launch, or SR-71.

I was fortunate to be surrounded by sharp, jovial, and supportive colleagues:
Ben had unprecedented simulation ideas;
Anand esoteric book recommendations;
Max cookies;
Dimitri sensational wit and a powerful \verb|c_avg| formulation;
Spencer cubes, a ray-tracing showcase, a shearing claim to rule, and \verb|.md| commits;
and Esteban \textit{complexified} papers he beheld.

Lastly, I must thank my family:
my father, Daniel, for his incredible selflessness;
my brother, Romain, for our deep discussions;
my mother Maria, and brother Vincent, for their unwavering belief in my academic persuits;
and my grandparents Virginia, Warren, Paulette, and Daniel for their love beyond
borders and time.

\renewcommand{\arraystretch}{1.2}

\vspace*{\fill}

\vspace{1cm}
\begin{center}
\textit{``And after all, we're only ordinary men.''} \\
\textit{--- Pink Floyd, Us and Them (1973)}
\end{center}
\vspace{1cm}

\vspace*{\fill}